A Generic and Efficient E-field Parallel Imaging Correlator for Next-Generation Radio Telescopes

### 2016-08-05 imaging_demo/ms.tex
Add, remove and update figures as per review
From df79977 (mnras):
====================

Update figures as per referee report

In ms.tex,

(*) Add, remove and update figures as per referee report

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
% \usepackage{mathptmx}
% \usepackage{txfonts}

@@

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage[flushleft]{threeparttable} % For table notes

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure5}
  % \includegraphics[width=\columnwidth]{autocorr_uvwts_pbeam}
  % \includegraphics[width=\columnwidth]{autocorr_uvwts_pbeam.png}
  \caption{The auto-correlation of weights of a square shaped antenna aperture
    in the $uv$ plane (left) and the corresponding directional antenna power 
    response on the sky (right) in coordinates specified by direction cosines. 
    The antenna auto-correlation weights are normalized to a sum
    of unity yielding a peak response of unity in the antenna's directional
    power pattern on the sky. The color scale for the directional power 
    pattern is logarithmic. The black circle indicates the sky horizon and
    values beyond it are not physical and hence ignored.}
  \label{fig:autocorr_wts_PB}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure6}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_10_random_source_positions_4_iterations_test_aperture_zoomed}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_10_random_source_positions_4_iterations_test_aperture_zoomed.eps}
  \caption{Dirty images (top) and synthesized beams (bottom) obtained from 
    simulated data using EPIC implementation of antenna-based MOFF algorithm 
    (left) and visibility-based imaging (right). The solid black circles in the
    top panels indicate the simulated source positions. The antenna 
    auto-correlations at zero-spacing have been removed from the MOFF images. 
    The images in either case reconstruct the sources at the right locations 
    with the fluxes expected after multiplication by the antenna power pattern. 
    The synthesized beams from the two algorithms are well matched in size and
    shape. The overall modulation by the power pattern is seen clearly in both
    images.}
  \label{fig:MOFF-FX-image}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure7}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_uvwts_test_aperture_zero_spacing_removed}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_uvwts_test_aperture_zero_spacing_removed.eps}
  \caption{Comparison of $uv$ plane antenna power response with MOFF (left) and 
    visibility-based imaging (right). The zero-spacing footprint from the $uv$ 
    weights obtained with MOFF has been subtracted. Differences in the void 
    centreed around zero-spacing and other outer regions is due to loss of 
    sampled antenna footprint precision due to coarseness of grid spacing 
    further made severe by the correlation process.}
  \label{fig:MOFF-FX-uvwts}
\end{figure}

@@

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure10}
  % \includegraphics[width=\columnwidth]{MOFF_FX_computations_fov_gridding_annotated}
  % \includegraphics[width=\columnwidth]{MOFF_FX_computations_fov_gridding_annotated.eps}
  \caption{Current and planned instruments in parameter space of
    number of complex multiplies and adds with MOFF and FX. The solid line
    is the boundary at which the number of operations with MOFF and 
    visibility-based imaging are equal. MOFF imaging is more efficient for 
    telescopes occupying the left of this line and vice versa. CHIME, HIRAX, 
    SKA1-LC, SKA1-LCD and all the HERA layouts except HERA-19 and HERA-37 lie 
    in the parameter space favoured by MOFF imaging. The dashed line shows the 
    projected trajectory of hypothetical expanded HERA layouts. The dotted line 
    similarly shows hypothetical expanded MWA layouts with more tiles added in 
    the same core. The gray shaded area denotes the projected trajectory of the 
    LWA bounded by LWA1 (left edge), LWA-OV (right edge), current layout 
    (bottom) and a four-fold increase in the number of elements within a 50 per 
    cent increase in the core size (top). Current instruments such as MWA and 
    LOFAR fall in a region favoured by visibility-based imaging.}
  \label{fig:parameter-space-computations-instruments}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure11}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended.eps}
  \caption{Current and planned instruments in parameter space of
    baseline length and number of antennas with MOFF and FX. Line styles of 
    different colors denote different classes of antenna sizes (cyan - 1~m$^2$, 
    blue - 7~m$^2$, purple - 16~m$^2$, green - 28~m$^2$, orange - 150~m$^2$, 
    red - 740~m$^2$, gray - 5900~m$^2$). Solid line style in each color denotes 
    the maximum number of antennas with the corresponding antenna size that can 
    be packed inside various baseline lengths. The region to the right of the 
    solid lines for corresponding antenna size is physically disallowed. Dashed
    lines of each color denote the boundary to the left of which 
    visibility-based imaging is favoured for the corresponding antenna size. 
    Region inside the wedge enclosed by the solid and dashed lines favours using 
    the MOFF algorithm for the corresponding antenna size. These wedges shift 
    leftward with increasing antenna size. The different antennas are color 
    coded by roughly the class of antenna size they fall into. Thus symbols of 
    one color falling into a wedge of the same color indicates MOFF imaging is 
    advantageous for those telescopes and vice versa. For example, MOFF imaging
    is favoured in HERA-331 and HERA-6769 because they are inside the wedge 
    but not so in cases of HERA-19 and HERA-37.}
  \label{fig:parameter-space-bll-nant-instruments}
\end{figure}

>>>>

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
% \usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
% \usepackage{mathptmx}
% \usepackage{txfonts}

@@

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage[flushleft]{threeparttable} % For table notes
\usepackage[caption=false]{subfig} % For subfloats

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure4}
  % \includegraphics[width=\columnwidth]{autocorr_uvwts_pbeam}
  % \includegraphics[width=\columnwidth]{autocorr_uvwts_pbeam.png}
  \caption{The auto-correlation of weights of a square shaped antenna aperture
    in the $uv$ plane (left) and the corresponding directional antenna power 
    response on the sky (right) in coordinates specified by direction cosines. 
    The antenna auto-correlation weights are normalized to a sum
    of unity yielding a peak response of unity in the antenna's directional
    power pattern on the sky. The color scale for the directional power 
    pattern is logarithmic. The black circle indicates the sky horizon and
    values beyond it are not physical and hence ignored.}
  \label{fig:autocorr_wts_PB}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure5}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_10_random_source_positions_4_iterations_test_aperture_zoomed}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_10_random_source_positions_4_iterations_test_aperture_zoomed.eps}
  \caption{Dirty images (top) and synthesized beams (bottom) obtained from 
    simulated data using EPIC implementation of antenna-based MOFF algorithm 
    (left) and visibility-based imaging (right). The solid black circles in the
    top panels indicate the simulated source positions. The antenna 
    auto-correlations at zero-spacing have been removed from the MOFF images. 
    The images in either case reconstruct the sources at the right locations 
    with the fluxes expected after multiplication by the antenna power pattern. 
    The synthesized beams from the two algorithms are well matched in size and
    shape. The overall modulation by the power pattern is seen clearly in both
    images.}
  \label{fig:MOFF-FX-image}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figure6}
  \caption{.}
  \label{fig:f-engine}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure7}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_uvwts_test_aperture_zero_spacing_removed}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_uvwts_test_aperture_zero_spacing_removed.eps}
  \caption{.}
  \label{fig:MOFF-FX-uvwts}
\end{figure}

@@

\section{Imaging with Heterogeneous Antenna Array}\label{sec:versatility}

\begin{figure*}
\subfloat[][Simulated Image]{\label{fig:nonphysical-image}\includegraphics[width=0.5\linewidth]{figure10a.eps}}
\subfloat[][Normalized Radial Flux Density Profile]{\label{fig:norm-flux-density}\includegraphics[width=0.42\linewidth]{figure10b.eps}}
\caption{.}
\label{fig:versatility}
\end{figure*}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure11}
  % \includegraphics[width=\columnwidth]{MOFF_FX_computations_fov_gridding_annotated}
  % \includegraphics[width=\columnwidth]{MOFF_FX_computations_fov_gridding_annotated.eps}
  \caption{Current and planned instruments in parameter space of
    number of complex multiplies and adds with MOFF and FX. The solid line
    is the boundary at which the number of operations with MOFF and 
    visibility-based imaging are equal. MOFF imaging is more efficient for 
    telescopes occupying the left of this line and vice versa. CHIME, HIRAX, 
    SKA1-LC, SKA1-LCD and all the HERA layouts except HERA-19 and HERA-37 lie 
    in the parameter space favoured by MOFF imaging. The dashed line shows the 
    projected trajectory of hypothetical expanded HERA layouts. The dotted line 
    similarly shows hypothetical expanded MWA layouts with more tiles added in 
    the same core. The gray shaded area denotes the projected trajectory of the 
    LWA bounded by LWA1 (left edge), LWA-OV (right edge), current layout 
    (bottom) and a four-fold increase in the number of elements within a 50 per 
    cent increase in the core size (top). Current instruments such as MWA and 
    LOFAR fall in a region favoured by visibility-based imaging.}
  \label{fig:parameter-space-computations-instruments}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure12}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended.eps}
  \caption{Current and planned instruments in parameter space of
    baseline length and number of antennas with MOFF and FX. Line styles of 
    different colors denote different classes of antenna sizes (cyan - 1~m$^2$, 
    blue - 7~m$^2$, purple - 16~m$^2$, green - 28~m$^2$, orange - 150~m$^2$, 
    red - 740~m$^2$, gray - 5900~m$^2$). Solid line style in each color denotes 
    the maximum number of antennas with the corresponding antenna size that can 
    be packed inside various baseline lengths. The region to the right of the 
    solid lines for corresponding antenna size is physically disallowed. Dashed
    lines of each color denote the boundary to the left of which 
    visibility-based imaging is favoured for the corresponding antenna size. 
    Region inside the wedge enclosed by the solid and dashed lines favours using 
    the MOFF algorithm for the corresponding antenna size. These wedges shift 
    leftward with increasing antenna size. The different antennas are color 
    coded by roughly the class of antenna size they fall into. Thus symbols of 
    one color falling into a wedge of the same color indicates MOFF imaging is 
    advantageous for those telescopes and vice versa. For example, MOFF imaging
    is favoured in HERA-331 and HERA-6769 because they are inside the wedge 
    but not so in cases of HERA-19 and HERA-37.}
  \label{fig:parameter-space-bll-nant-instruments}
\end{figure}
